Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2015-10-25 Docs/TODAES/paper.tex
minor changes

%\begin{listing}[H]
%\begin{minted}[mathescape,
%               linenos,
%               numbersep=7pt,
%               gobble=0,
%               frame=lines,
%               framesep=2mm]{c++}
%  GetNextStep(){
%  int largestChunk = -1;
%  chunk largest;
%  for each(chunk in chunks){
%     if(chunk.right - chunk.left > largestChunk){
%           largestChunk = chunk.right - chunk.left;
%           largest = chunk;
%     }
%   }	
%   chunks.remove(largest);	
%   int median = largest.left + floor((largest.right - largest.left) / 2)
%   if(median > 0){
%      if(largest.right - largest.left > 1)
%         chunks.add(new chunk(largest.left, median - 1));	
%      if(largest.right != largest.left)
%         chunks.add(new chunk(median + 1, largest.right);
%    }
%   return median;
% }
%\end{minted}
%\caption{Steps calculation using intervals.}
%\label{Steps-Calculation-using-Intervals}
%\end{listing}
\vspace {2 mm}
\begin{lstlisting}[basicstyle=\small,caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
GetNextStep(){
  int largestChunk = -1;
  chunk largest;
  for each(chunk in chunks){
    if(chunk.right - chunk.left > largestChunk){
      largestChunk = chunk.right - chunk.left;
      largest = chunk;
    }
  }	
  chunks.remove(largest);	
  int median = largest.left + floor((largest.right - largest.left) / 2)
  if(median > 0){
    if(largest.right - largest.left > 1)
      chunks.add(new chunk(largest.left, median - 1));	
    if(largest.right != largest.left)
      chunks.add(new chunk(median + 1, largest.right);
  }
  return median;
}
\end{lstlisting}

@@

\bibliographystyle{ACM-Reference-Format-Journals}
\bibliography{Ref.bib}

>>>>

%\begin{listing}[H]
%\begin{minted}[mathescape,
%               linenos,
%               numbersep=7pt,
%               gobble=0,
%               frame=lines,
%               framesep=2mm]{c++}
%  GetNextStep(){
%  int largestChunk = -1;
%  chunk largest;
%  for each(chunk in chunks){
%     if(chunk.right - chunk.left > largestChunk){
%           largestChunk = chunk.right - chunk.left;
%           largest = chunk;
%     }
%   }	
%   chunks.remove(largest);	
%   int median = largest.left + floor((largest.right - largest.left) / 2)
%   if(median > 0){
%      if(largest.right - largest.left > 1)
%         chunks.add(new chunk(largest.left, median - 1));	
%      if(largest.right != largest.left)
%         chunks.add(new chunk(median + 1, largest.right);
%    }
%   return median;
% }
%\end{minted}
%\caption{Steps calculation using intervals.}
%\label{Steps-Calculation-using-Intervals}
%\end{listing}
\vspace {2 mm}
\begin{lstlisting}[basicstyle=\small,caption={Steps calculation using intervals.},label={Steps-Calculation-using-Intervals},numbersep=7pt,frame=tb,captionpos=b,numbers=left,numberstyle=\tiny]
GetNextStep(){
  int largestChunk = -1;
  chunk largest;
  for each(chunk in chunks){
    if(chunk.right - chunk.left > largestChunk){
      largestChunk = chunk.right - chunk.left;
      largest = chunk;
    }
  }	
  chunks.remove(largest);	
  int median = largest.left + floor((largest.right - largest.left) / 2);
  if(median > 0){
    if(largest.right - largest.left > 1)
      chunks.add(new chunk(largest.left, median - 1));	
    if(largest.right != largest.left)
      chunks.add(new chunk(median + 1, largest.right);
  }
  return median;
}
\end{lstlisting}

@@

\bibliographystyle{ACM-Reference-Format-Journals}
\bibliography{Ref}
